---
title: "Untitled"
output: word_document
date: "2024-10-29"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Data Processing

describe how the data were cleaned 
Convert to numeric

```{r}
nor_analytic <- nor |> dplyr::filter(!is.na(`Discirmination Index`)) |>
  dplyr::rename(Litter = `Litter ID`)
```


# Summary statistics

summary table of NOR discrimination by Tx group, add overall

```{r}
discrim_tx_tbl <- nor |>
  dplyr::select(
    Treat, `Discirmination Index`
  ) |>
  gtsummary::tbl_summary(
    by = Treat,
    type = list(
      `Discirmination Index` ~ "continuous2"
    ),
    statistic = list(
      gtsummary::all_continuous2() ~ c(
        "{mean} ({sd})",
        "{median} [{p25}, {p75}]",
        "{min}, {max}"
      )
    )
  ) |>
  gtsummary::add_overall()

discrim_tx_tbl


discrim_tx_sex_tbl <- nor_analytic |>
  dplyr::select(
    Treat, `Discirmination Index`, Sex
  ) |>
  gtsummary::tbl_strata(
    strata = Sex,
    .tbl_fun = 
      ~ .x |>
      gtsummary::tbl_summary(
        by = Treat,
        type = list(
          `Discirmination Index` ~ "continuous2"
        ),
        statistic = list(
          gtsummary::all_continuous2() ~ c(
            "{mean} ({sd})",
            "{median} [{p25}, {p75}]",
            "{min}, {max}"
          )
        )
      ) |>
      gtsummary::add_overall() |>
      gtsummary::modify_header(
        gtsummary::all_stat_cols() ~ "**{level}**"
      ),
    .combine_with = 'tbl_stack'
  )

discrim_tx_sex_tbl
```

histogram

```{r}
nor_plot_data <- dplyr::bind_rows(
  nor_analytic, 
  nor_analytic |> dplyr::mutate(Treat = "Overall")
) |>
  dplyr::mutate(
    Treat = factor(
      Treat,
      levels = c(
        "Adjuvant+Saline", "CRMP1+CRMP2",
        "CRMP1+GDA", "LDHA+LDHB+CRMP1+STIP1",
        "STIP1+NSE", "Overall"
      )
    )
  )

cowplot::plot_grid(
  ggplot2::ggplot(
    data = nor_analytic,
    ggplot2::aes(x = `Discirmination Index`)
  ) +
  ggplot2::geom_histogram() +
  ggplot2::theme_bw(),
  ggplot2::ggplot(
    data = nor_plot_data,
    ggplot2::aes(x = `Discirmination Index`)
  ) +
  ggplot2::geom_histogram() +
  ggplot2::facet_wrap(
    .~Treat
  ) +
  ggplot2::theme_bw(),
  nrow = 2
)

```

# Model results


discrimination index is bounded by [0, 1]

mixed effect model with fixed effect for treatment group and random intercept for litter

ANOVA type 3 p-value for Tx
Model summary table

Check model diagnostic plots

```{r}
fit <- lmerTest::lmer(
  `Discirmination Index` ~ Treat + (1|Litter),
  data = nor_analytic
)

car::Anova(fit, type = 3)

sjPlot::tab_model(fit)

performance::check_model(fit)
```

```{r}
fit_sex_intrxn <- lmerTest::lmer(
  `Discirmination Index` ~ Treat*Sex + (1|Litter),
  data = nor_analytic
)

car::Anova(fit_sex_intrxn, type = 3)

sjPlot::tab_model(fit_sex)

performance::check_model(fit_sex)
```

```{r}
fit_sex <- lmerTest::lmer(
  `Discirmination Index` ~ Treat + Sex + (1|Litter),
  data = nor_analytic
)

car::Anova(fit_sex, type = 3)

sjPlot::tab_model(fit, fit_sex)

performance::check_model(fit_sex)

```
